Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-09-27 saner/paper.tex
Added some stuff to the paper

To detect automatically refactorable clones, we propose to:
\begin{itemize}
  \item Compare variable references not only by their name but also by their type.
  \item Compare referenced types by their fully qualified identifier (FQI). The FQI of a type reference describes the full path to where it is declared.
  \item Compare method references by their fully qualified signature (FQS). The FQS of a method reference describes the full path to where it is declared, plus the FQI of each of its parameters.
\end{itemize}

>>>>

To detect automatically refactorable clones, we propose to:
\begin{itemize}
  \item Compare types by their fully qualified identifier (FQI). The FQI of a type reference describes the full path to where it is declared.
  \item Compare variable references not only by their name but also by their type (FQI).
  \item Compare method references by their fully qualified signature (FQS). The FQS of a method reference describes the full path to where it is declared, plus the FQI of the type of each of its parameters.
\end{itemize}
